Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-22 paper.qmd
Added umap projection for Gaussian clusters..need to scale data first

@@

five_gau_proj_umap_model <- projected_df |>
  filter(type == "data") |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        alpha = 0.3) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55)) +
  interior_annotation("b", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

```{r}
#| label: fig-five-gau-projs
#| fig-height: 6
#| fig-width: 18
#| fig-cap: "(a) tSNE, (b) UMAP, and (c) PaCMAP"

five_gau_proj_tsne_model + five_gau_proj_umap_model + five_gau_proj_pacmap_model +
  plot_layout(guides = "collect", ncol = 3) &
  theme(legend.position='none')
```

>>>>

## First projection
projection <- cbind(
    c(0.18827,-0.28588,-0.20848,-0.78132),
    c(0.71366,0.00788,-0.42630,0.28283))

@@

five_gau_proj_umap_model1 <- projected_df |>
  filter(type == "data") |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        alpha = 0.3) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.12, 0.12)) +
  interior_annotation("b", 
                      position = c(0.08, 0.9),
                      cex = 3)

## Second projection
projection <- cbind(
  c(0.58453,-0.38194,0.05395,0.52974),
  c(0.29917,0.29629,-0.76964,-0.03810))

five_gau_proj_umap_model2 <- projected_df |>
  filter(type == "data") |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        alpha = 0.3) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  xlim(c(-0.16, 0.1)) +
  ylim(c(-0.1, 0.1)) +
  interior_annotation("b", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

```{r}
#| label: fig-five-gau-projs
#| fig-cap: "(a) tSNE, (b) UMAP, and (c) PaCMAP"

# fig-height: 6 
# fig-width: 18

five_gau_proj_tsne_model + five_gau_proj_tsne_model +
  five_gau_proj_umap_model1 + five_gau_proj_umap_model2 +
  five_gau_proj_pacmap_model + five_gau_proj_pacmap_model +
  plot_layout(guides = "collect", ncol = 2) &
  theme(legend.position='none')
```
